%%-*-latex-*-

\documentclass[a4paper,11pt,twoside]{article}

\usepackage[landscape]{geometry}

% Language and fonts
%
\usepackage[british]{babel}    % British English
\usepackage[T1]{fontenc}       % Required for hyphenation and \DJ
\usepackage[utf8]{inputenc}    % UTF-8 encoding
%\usepackage{hyphenat}          % \hyp{} is a breakable dash
%\usepackage{url}               % To typeset URLs
%\usepackage{mdwlist}           % Tight vertical spacing of list items
%\usepackage{microtype}         % Microtypographic enhancements
\usepackage{textcomp}          % For Numero abbreviation

\hfuzz 2pt % Do not report overhang less than 2pt

%--------------------------------------------------------------------
%
\begin{document}

\pagestyle{empty}

\begin{center}
\textsc{French Republic}\\
\textsc{Ministry of national education, youth and sports}\\
\textsc{University Pierre and Marie Curie (Paris~6)}\\
\ \\
\textsc{\Large MASTER'S (SECOND YEAR)}\\
\ \\
in theoretical informatics, computing and programming.\\
\ \\
(Ordinance of 23~November 1988 regulating doctoral studies)
\end{center}
Given the ministerial ordinance dated 13~March 1986 granting the
University Pierre and Marie Curie (Paris~VI) the right to deliver the
diploma of second year of master's degree in theoretical informatics,
computing and programming.

\medskip

Given the initial diplomas presented by Mr~Christian Rinderknecht,
born 6~February 1970 at Beaumont-sur-Oise (Val d'Oise);

\medskip

Given the documents attesting that the grantee passed the examinations
on the theoretical and methodological courses and to the introduction
to the research techniques whose details are inscribed at the back of
the present diploma;

\medskip

The diploma of second year of master's degree in theoretical
informatics, computing and programming is hereby granted to Mister
Christian Rinderknecht to be enjoyed with all rights and privileges
pertaining thereto.

\bigskip

Paris, 17~January 1994.

\bigskip

[Signed by] The president of the university Paris~VI, J.C. Legrand.

[Signed by] The grantee, Christian Rinderknecht.

Approved, on behalf of the Minister, by the Rector of the Academy,
Chancellor of the Universities [Signature].

\bigskip

\hfill\textnumero~75~VI~544

\newpage

\begin{center}
\sc Kind of the examinations and internship\\
which the grantee of the present diploma has passed.
\end{center}

\medskip

\begin{center}
\begin{tabular}{|l|c|l|}
\hline
\multicolumn{1}{|c|}{Topic} & Dates of validation & Observations\\
\hline
Object-oriented programming & June 1993 & Internship\\
Introduction to computer algebra & June 1993 & \\
Analyse d'algorithmes & June 1993 &\\
\hline
\end{tabular}
\end{center}

\medskip

The secretary-general of the University Paris~VI hereby certifies the
veracity of and state the present list made of~3 examinations or
completed internships.

\medskip

[Signed by] P.~Endrivet \hfill Paris, 18~January 1994.

\end{document}
