%%-*-latex-*-

\documentclass[a4paper,11pt,twoside]{article}

%\usepackage[landscape]{geometry}

% Language and fonts
%
\usepackage[british]{babel}    % British English
\usepackage[T1]{fontenc}       % Required for hyphenation and \DJ
\usepackage[utf8]{inputenc}    % UTF-8 encoding
%\usepackage{hyphenat}          % \hyp{} is a breakable dash
%\usepackage{url}               % To typeset URLs
\usepackage{mdwlist}           % Tight vertical spacing of list items
%\usepackage{microtype}         % Microtypographic enhancements
\usepackage{textcomp}          % For Numero abbreviation

\hfuzz 2pt % Do not report overhang less than 2pt

%--------------------------------------------------------------------
%
\begin{document}

\thispagestyle{empty}

\begin{flushleft}
University Pierre and Marie Curie~-~Paris~VI\\
\textsc{Faculty of Informatics~922}\\
\ \\
Institut of Programmation\\
All\'ee 55-65\\
4, Place Jussieu\\
75252 Paris Cedex~05\\
\ \\
Tel: (33) (1)~44~27~53~93\\
Fax: (33) (1)~44~27~62~86
\end{flushleft}

\bigskip\bigskip

\begin{center}
\textsc{\Large Transcripts}
\end{center}

\bigskip

I, Jacques Sakarovitch, Director of Research at the CNRS, head of the
second year of the master's program \emph{Theoretical informatics,
  Computing and Programming}, hereby testifies that Mr~Christian
Rinderknecht obtained the following scores:

\bigskip

\noindent\textbf{Mandatory courses: 13.83/20} 
\begin{itemize*}

  \item Combinatoric algorithms --~J.~Berstel: 10/20.

  \item Automata and formal languages --~J.~Sakarovitch: 12/20.

  \item Semantics and theory of programming --~R.~Robinet: 18/20.

  \item Methods of translation --~B.~Lorho: 14/20.

  \item Introduction to object-oriented programming --~Ph.~Gautron:
    16/20.

  \item Foundations of computer algebra --~D.~Lazard: 13/20.

\end{itemize*}

\bigskip

\noindent\textbf{Optional courses: 15.67/20} (average of the best
three scores).
\begin{itemize*}

  \item In the minor ``Programming'':
    \begin{itemize*}

      \item Object-oriented programming --~Ph.~Gautron: 14.5/20.
      
      \item $\lambda$-calculus and compilation of functional languages
        --~Th.~Hardin \& D.~Vidal: 16/20.

      \item Rewrite systems --~Th.~Hardin: 16/20.

    \end{itemize*}

  \item In the minor ``Computing'':
    \begin{itemize*}

      \item Analysis of algorithms --~M.~Soria: 15/20.

    \end{itemize*}

\end{itemize*}

\bigskip

\noindent\textbf{Internship: On-going.}

\bigskip

\hfill[Signed by] J.~Sakarovitch, Head of the second year of the
master's program ITCP.

\bigskip

\hfill Paris, 15 July 1993.

\end{document}
